The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2020-07-29 Writeup/manuscript.tex
Fixed some typos

\subsection*{Participants}
Twenty-five participants (11 females, mean age 28.7±13.3) took part in the EEG experiment. Their informed consent was obtained before the experiment under a protocol that was approved by the Institutional Review Board of Stanford University. 11 participants (8 females mean age 20.73±1.21) took part in the psychophysics experiment. All participants had normal or corrected-to-normal vision. Their informed consent was obtained before the experiment under a protocol that was approved by the University of Essex's Ethics Committee.

@@

\subsection*{Psychophysics Procedure}
The experiment consisted of 16 blocks, one for each of the wallpaper groups (excluding $P1$). In each trial, participants were presented with two stimuli (one of which was the wallpaper group for the current block of trials, the other being $P1$), one after the other (inter stimuli interval of 700ms). After each stimuli had been presented, it was masked with white noise for 300ms. After both stimuli had been presented, participants made a response on the keyboard to indicate whether they thought the first or second contained the most symmetry. Each block started with 10 practise trials, (stimulus display duration of 500ms) to allow participants to familiarise themselves with the current block's wallpaper pattern. If they achieved an accuracy of 9/10 in these trials they progressed to the rest of the block, otherwise they carried out another set of 10 practise trials. This process was repeated until the required accuracy of 9/10 was obtained. The rest of the block consisted of four interleaved staircases (using the QUEST algorithm \cite{watson1983quest}, full details given in the SI) of 30 trials each. on average, a block of trials took around 10 minutes to complete.

@@

\subsection*{Bayesian Analysis of EEG and Psychophysical data}
Bayesian analysis was carried out using R (v3.6.1) \cite{R} with the \texttt{brms} package (v2.9.0 \cite{burkner2017} and rStan (v2.19.2 \cite{rStan}). The data from each experiment were modelled using a Bayesian generalised mixed effect model with wallpaper group being treated as a 16 level factor, and random effects for participant. The EEG data and display thresholds were modelled using log-normal distributions with weakly informative ($N(0, 2)$) priors. After fitting the model to the data, samples were drawn from the posterior distribution for each mean of the EEG response (display duration) for each wallpaper group. These samples were then recombined to calculate the distribution of differences for each pair of subgroup and super-group. These distributions were then summarised by computing the conditional probability that of obtaining a positive (negative) difference, $p(\Delta | data)$.

For further technical details, please see the supplementary materials where the full R code and model specification can be found.

>>>>

\subsection*{Participants}
Twenty-five participants (11 females, mean age 28.7±13.3) took part in the EEG experiment. Their informed consent was obtained before the experiment under a protocol that was approved by the Institutional Review Board of Stanford University. 11 participants (8 females, mean age 20.73±1.21) took part in the psychophysics experiment. All participants had normal or corrected-to-normal vision. Their informed consent was obtained before the experiment under a protocol that was approved by the University of Essex's Ethics Committee.

@@

\subsection*{Psychophysics Procedure}
The experiment consisted of 16 blocks, one for each of the wallpaper groups (excluding $P1$). In each trial, participants were presented with two stimuli (one of which was the wallpaper group for the current block of trials, the other being $P1$), one after the other (inter stimuli interval of 700ms). After each stimuli had been presented, it was masked with white noise for 300ms. After both stimuli had been presented, participants made a response on the keyboard to indicate whether they thought the first or second contained the most symmetry. Each block started with 10 practise trials, (stimulus display duration of 500ms) to allow participants to familiarise themselves with the current block's wallpaper pattern. If they achieved an accuracy of 9/10 in these trials they progressed to the rest of the block, otherwise they carried out another set of 10 practise trials. This process was repeated until the required accuracy of 9/10 was obtained. The rest of the block consisted of four interleaved staircases (using the QUEST algorithm \cite{watson1983quest}, full details given in the SI) of 30 trials each. On average, a block of trials took around 10 minutes to complete.

@@

\subsection*{Bayesian Analysis of EEG and Psychophysical data}
Bayesian analysis was carried out using R (v3.6.1) \cite{R} with the \texttt{brms} package (v2.9.0) \cite{burkner2017} and rStan (v2.19.2 \cite{rStan}). The data from each experiment were modelled using a Bayesian generalised mixed effect model with wallpaper group being treated as a 16 level factor, and random effects for participant. The EEG data and display thresholds were modelled using log-normal distributions with weakly informative, $ \mathcal{N}(0, 2)$, priors. After fitting the model to the data, samples were drawn from the posterior distribution for each mean of the EEG response (display duration) for each wallpaper group. These samples were then recombined to calculate the distribution of differences for each pair of subgroup and super-group. These distributions were then summarised by computing the conditional probability of obtaining a positive (negative) difference, $p(\Delta | data)$.

For further technical details, please see the supplementary materials where the full R code, model specification, prior and posterior predicitive checks, and model diagnoastics, can be found.
